Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-29 manuscript.Rmd
Edits to social cohesion and mobilization subsections

## Social Cohesion
Real-world collective action is known to bring about a sense of togetherness,
also known as “collective effervescence” [@durkheim1995elementary]. This
feeling of being a part of something larger than oneself leads individuals
to act in ways that would not have on their own. Being overcome with this
feeling is known to lead to violence [@collins2009violence; @spaaij2014sports].
While feelings of social connection may lead to violence, increased exposure
to violence can result in feelings of social cohesion. @gilligan2014civil
found that exposure to fatal wartime violence resulted in increased prosocial
motivations, including cooperative behaviors, feelings of trust, and overall
community-level social cohesion. Just as real-world social cohesion can be
quantified, the same is true for online cohesion. Strategic communication on
social media in the form of social cohesion of language can lead to real-world
social change, and exposure to real-world violence could result in social
cohesion in the virtual world. Increased social cohesion is thus potentially
an indicator of increased social organization and mobilization on the ground.

## Social Media as a Platform for Mobilization
Social media platforms, such as Twitter, offer rapid real-time dissemination
of information. Given its accessibility and proficiency as an information
exchange tool, individuals involved in social movements have taken to them
in conjunction, or in replacement, of real-world social mobilization.
During the 2012 Italian protests for global economic change, the riots in
Rome were mirrored by Twitter activity both on the same day and in the
following days after the protests [@vicari2013public]. Tweeting was
determined to be more effective locally in discussing real-world, real-time
events than traditional mainstream media platforms. As more and more
individuals rely on social media to obtain local news and information, it
becomes increasingly important to understand just how these micro-blogs
reflect real-world action.

>>>>

## Social Cohesion and Social Mobilization
Real-world collective action is known to bring about a sense of togetherness,
also known as “collective effervescence” [@durkheim1995elementary]. This
feeling of being a part of something larger than oneself leads individuals
to act in ways that would not have on their own. Being overcome with this
feeling can lead to violence [@collins2009violence; @spaaij2014sports].
Conversely, increased exposure
to violence can result in positive social cohesion. @gilligan2014civil
found that exposure to fatal wartime violence resulted in increased prosocial
motivations, including cooperative behaviors, feelings of trust, and overall
community-level social cohesion.

Just as real-world social cohesion can be
quantified, so can online cohesion. While this can be quantified in many ways,
one kind of cohesion can be found in the similarity in language use on social media.
This implicit or explicit similarity in language use can indicate shared
beliefs, thoughts, and feelings, as has been studied in research on language style
in psycholinguistics and social psychology 
[@gonzales2010language, @tausczik2010psychological, @brennan1996conceptual]; 
although previous work on language style
has often focused on individuals and small groups, this can be scaled up to examine
massive social-level changes [@michel2011quantitative, @fusaroli2015timescales]. 
This kind of massive online social cohesion can lead to real-world
social change.

Combining these separate threads, it is reasonable to expect that real-world actions 
and online social interactions would be enmeshed, driving and being driven by 
one another. Rather than expecting that only real-world social cohesion would be
driven by real-world action, we would expect interaction between real-world and
virtual dynamics: In this case, exposure to real-world violence could result in social
cohesion in the virtual world. Increased social cohesion is thus potentially
an indicator and a result of increased social organization and mobilization 
on the ground.

Social media platforms provide one way of enabling this kind of online social
cohesion by offering distributed information-gathering and real-time information
dissemination. Given its accessibility and proficiency as an information
exchange tool, Twitter has provided individuals involved in social movements
an opportunity to complement or even replace real-world social mobilization.
For example, during the 2012 Italian protests for global economic change, the riots in
Rome were mirrored by Twitter activity both on the day of the protests and in the
days following them [@vicari2013public]. Tweeting was
determined to be more effective locally in discussing real-world, real-time
events than traditional mainstream media platforms. As more and more
individuals rely on social media to obtain local news and information, it
becomes increasingly important to understand just how these micro-blogs
reflect real-world action.
